Leveraging open platforms to manage and distribute streams of versioned data

### 2017-04-26 ms.tex
Clean up GH urls; remove break after  title page

\newcommand{\datastorr}{\texttt{datastorr}}
\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
\newcommand{\ghsmurl}[1]{{\footnotesize\href{}{#1}}}

@@

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item Data is cool
\end{enumerate}

\section{Overview}

Main aims of paper:

\begin{enumerate}
  \item Recognise need for versioned datasets
  \item Provide workflow / infrastructure for people to distribute and access small-medium sized data with minimal setup and cost, by leveraging emerging technologies
\end{enumerate}

% Access point might change, e.g. github goes out of business

% Workflows for dataset assembly: One or two packages? More complex like baad has two packages. Taxonlookup is all in one

@@

To distribute/retrieve versioned data releases from Github, we have developed
a  work flow that enables dataset maintainers to write a customised R package
for their dataset. This workflow uses another R package called
\texttt{datastorr} to handle all the interactions with github. For example, the package
\texttt{baad.data} can retrieve data releases from the Biomass and Allometry Database, stored at \ghsmurl{github.com/dfalster/baad/} (see Table \ref{tab:examples} for more examples).

@@

\section{Table}

@@

\begin{table}[h!]
\centering
\caption{Alternative platforms for minting DOIs from github repositories}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{3cm}p{8cm}}
  \hline
  \textbf{Provider} & \textbf{Features} \\ \hline
  \multicolumn{2}{l}{Zenodo: zenodo.org}\\
    & Automated DOI for each github release \\
    & Funded and maintained by CERN and OpenAIRE for long term preservation \\
    & Only includes files embedded in git repo, not built  by code\\
  \multicolumn{2}{l}{Figshare: figshare.com}\\
    & Builds data package based on github release \\
    & Allows you to upload additional files, e.g. datasets built by code \\
    & Integrated with several journals, e.g. Nature family, PNAS \\
    & Some limited potential for versioned DOIs\\
  \hline
  \end{tabular}
  }
\label{tab:doi_minting}
\end{table}

@@

  \begin{tabular}{p{7cm}p{4cm}p{2cm}}
  \hline
   \textbf{URL} & \textbf{R package} & \textbf{Description} \\ \hline
  \ghsmurl{github.com/dfalster/baad/} & \texttt{baad.data} & The \texttt{Biomass And Allometry Database} \citep{Falster-2015} provides...\\
  \ghsmurl{github.com/traitecoevo/taxonlookup} & \texttt{taxonlookup} & \texttt{taxonlookup} \citep{Pennell-2015a} provides...\\
  \ghsmurl{github.com/...} & \texttt{plantgrowthform}  & \texttt{plantgrowthform} provides... \\
  \ghsmurl{github.com/...} & \texttt{fungaltraits} & \texttt{fungaltraits} (in progress) provides... \\
  \ghsmurl{github.com/...} & \texttt{13C} & \texttt{13C} (in progress) provides .... \\
  \hline
  \end{tabular}
  }
\label{tab:examples}
\end{table}

>>>>

\newcommand{\datastorr}{\texttt{datastorr}}
\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
\newcommand{\ghsmurl}[1]{{\footnotesize\href{https://github.com/#1}{#1}}}

@@

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item Data is cool.
\item Recognise need for versioned datasets
\item Provide workflow / infrastructure for people to distribute and access small-medium sized data with minimal setup and cost, by leveraging emerging technologies
\end{enumerate}

@@

To distribute/retrieve versioned data releases from Github, we have developed
a  work flow that enables dataset maintainers to write a customised R package
for their dataset. This workflow uses another R package called
\texttt{datastorr} to handle all the interactions with github. For example, the package
\texttt{baad.data} can retrieve data releases from the Biomass and Allometry Database, stored at \smurl{github.com/dfalster/baad/} (see Table \ref{tab:examples} for more examples).

@@

\section{Tables}

@@

\begin{table}[h!]
\centering
\caption{Alternative platforms for minting DOIs from github repositories}
{\footnotesize
\vspace{1cm}
  \begin{tabular}{p{4cm}p{8cm}}
  \hline
  \textbf{Provider} & \textbf{Features} \\ \hline
  Zenodo: \smurl{zenodo.org} & Automated DOI for each github release \\
    & Funded and maintained by CERN and OpenAIRE for long term preservation \\
    & Only includes files embedded in git repo, not built  by code\\
  Figshare: \smurl{figshare.com} & Builds data package based on github release \\
    & Allows you to upload additional files, e.g. datasets built by code \\
    & Integrated with several journals, e.g. Nature family, PNAS \\
    & Some limited potential for versioned DOIs\\
  \hline
  \end{tabular}
  }
\label{tab:doi_minting}
\end{table}

@@

  \begin{tabular}{p{3.5cm}p{3cm}p{7cm}}
  \hline
   \textbf{Github repo} & \textbf{R package} & \textbf{Description} \\ \hline
  \ghsmurl{dfalster/baad/} & \texttt{baad.data} & The \texttt{Biomass And Allometry Database} \citep{Falster-2015} provides...\\
  \ghsmurl{traitecoevo/taxonlookup} & \texttt{taxonlookup} & \texttt{taxonlookup} \citep{Pennell-2015a} provides...\\
  \ghsmurl{github.com/...} & \texttt{plantgrowthform}  & \texttt{plantgrowthform} provides... \\
  \ghsmurl{github.com/...} & \texttt{fungaltraits} & \texttt{fungaltraits} (in progress) provides... \\
  \ghsmurl{github.com/...} & \texttt{13C} & \texttt{13C} (in progress) provides .... \\
  \hline
  \end{tabular}
  }
\label{tab:examples}
\end{table}
